On Misuses of the Kolmogorov–Smirnov-Test

### 2022-04-22 Manuscript/manuscript.tex
more detail in fitted+dependence section

The remedy using copulas is effective in the case where both assumptions are violated.
This is shown in Figure~\ref{fig:hist_copula}. The "super naive" plot is the resulting 
p-values when you naively use fitted parameters while ignoring dependence in the data.
The "naive parametric" plot is the result of applying parametric bootstrap to correct
for fitted parameters, as done in section \ref{fitted}. Of course, the "copula" plot 
applies the fix for both assumptions.

@@

We would also like to show that copulas work for more than a simple AR(1) model. 
Figure~\ref{fig:hist_copula_ma1} is the procedure performed on data generated from 
an MA(1) model with $\theta = 0.5$. Figure~\ref{fig:hist_copula_arma} is the procedure 
performed on data generated from an ARMA(1,1) model with $\psi = 0.5$ and $\theta = 0.3$. 
It is also possible to apply our procedure to other distributions. The data in Figure~\ref{fig:hist_copula_gamma} is generated from $Gamma ~ (3,1)$ with $\rho = 0.5$.

@@

@@

>>>>

The remedy using copulas is effective in the case where both assumptions are violated.
This is shown in Figure~\ref{fig:hist_copula}. The "super naive" plot is the resulting 
p-values when you naively use fitted parameters while ignoring dependence in the data.
The "naive parametric" plot is the result of applying parametric bootstrap to correct
for fitted parameters while ignoring potential dependence. Of course, the "copula" 
plot applies the fix for both assumptions. The results show that copula remedy generates 
uniform p-values and restores the power of the K-S test.

@@

The copula fix is not a complete solution, because regardless of the true dependence in the data
we assume an AR(1) model by taking the lag-1 sample auto-spearman rho. However, we can 
show that as long as the AR(1) assumption is a close approximation, the correction still restores power to the test.
Figure~\ref{fig:hist_copula_ma1} is the procedure performed on data generated from 
an MA(1) model with $\theta = 0.5$. Figure~\ref{fig:hist_copula_arma} displays results with 
data generated from an ARMA(1,1) model with $\psi = 0.5$ and $\theta = 0.3$.

@@

It is also possible to apply our procedure to other distributions. All of the simulations
to this point have been done with standard normal data. The data in Figure~\ref{fig:hist_copula_gamma} 
is generated from $Gamma ~ (3,1)$ with a correlation coefficient of $\rho = 0.5$. Figure~\ref{fig:hist_copula_gev}
shows the procedure applied to data from $GEV ~ (0, 0.2, 1)$ with a correlation coefficient of $\rho = 0.5$.

@@

Where this remedy falls short is when the approximation of an AR(1) model is too inaccurate.
An AR(2) model can be used to demonstrate this. For an AR(2) model with $\phi = (0.5, 0.3)$,
Figure~\ref{fig:hist_copula_ar2} displays the results of applying the various remedies. 
While the remedies improve the plot of the p-values in comparison to the naive case,
because the approximation is not close enough the correction does not work completely.
